\vspace{-1em}Guidance, Please! Towards a Framework for RDF-based Constraint Languages.

### 2015-08-12 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
unit-record

As we do not want to base our conclusions on the evaluation of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
For all these 115 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (DDI-RDF, QB, SKOS) obtained from 33 SPARQL endpoints.
%evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
Based on the evaluation results,
we formulate several hypotheses to direct the further development of constraint languages.
To make valid general statements for all vocabularies, however,
the hypotheses still have to be verified or falsified
by evaluating the quality of data represented by more than three vocabularies (Section \ref{evaluation}).
%The \textbf{contribution} of this paper is the development of a system 
%\begin{enumerate}
	%\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
	%\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
%\end{enumerate}
%By defining a huge amount of constraints of the majority of the constraint types,   
%we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
%A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
%We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
%how data in tabular format and metadata on record-unit data sets, aggregated data sets, and thesauri are represented in RDF, 
%how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
%and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
%We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding 
%(1) which sets of constraint types (on different levels of complexity) and 
%(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).

@@

The data most often used in research within \emph{SBE} sciences is \emph{record-unit data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records, registers of births and deaths. A \emph{study} represents the process by which a data set was generated or collected. The range of record-unit data is very broad - including census, education, health data and business, social, and labor force surveys. This type of research data is held within data archives or data libraries after it has been collected, so that it may be reused by future researchers. By its nature, record-unit data is highly confidential and access is often only permitted for qualified researchers who must apply for access. Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns: so-called \emph{variables} such as \emph{sex} or \emph{age}. Aggregated data, which answers particular research questions, is derived from record-unit data by statistics on groups or aggregates such as frequencies and arithmetic means. The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying record-unit data. For more detailed analyses, researchers refer to record-unit data including additional variables needed to answer subsequent research questions.

@@

For more detailed analyses we refer to the underlying record-unit data. The aggregated variable \emph{formal childcare} is calculated on the basis of six record-unit variables (i.a., \emph{Education at pre-school}) for which detailed metadata is given (i.a., code lists) enabling researchers to replicate the results shown in aggregated data tables.
\emph{DDI-RDF} is used to represent metadata on record-unit data in RDF.
%The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
%\emph{dcterms:spatial} points to the countries for which the data has been collected.
The study (\emph{disco:Study}) for which the record-unit data has been collected 
%\emph{EU-SILC 2011} 
contains eight data sets (\emph{disco:LogicalDataSet})
including variables (\emph{disco:Variable}) like the six ones needed to calculate the variable \emph{formal childcare}.
%Metadata on record-unit data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
%One common research question is ,e.g., the comparison of variables like 
%\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).

@@

%The data most often used in research within \emph{SBE} sciences is \emph{record-unit data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers

@@

%The range of record-unit data is very broad - 

@@

%By its nature, record-unit data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 

@@

%Aggregated data, which answers particular research questions, is derived from record-unit data by statistics on groups or aggregates such as frequencies and arithmetic means.
%The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying record-unit data.

@@

%For more detailed analyses, researchers refer to record-unit data including additional variables needed to answer subsequent research questions

@@

%For more detailed analyses we refer to the record-unit data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}. 

@@

%The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on record-unit data in RDF.

@@

%The study \emph{EU-SILC 2011} contains eight record-unit data sets (\emph{DDI-RDF:LogicalDataSet})

@@

%%Validation environments should enable users to decide if they wish to perform reasoning prior to validation.
%%Reasoning as an optional pre validation step is beneficial for RDF validation as 
%%(1) it may resolve constraint violations and  
%%(2) it may cause useful constraint violations.
%A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
%%Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
%%\begin{DL}
%%Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
%%\end{DL}
%Consider the following DL knowledge base $\mathcal{K}$\footnote{A knowledge base is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly. For simplicity reasons, we only write namespace prefixes in DL statements to avoid ambiguities.}:
%
%\begin{center}
%\begin{DL} 
%$\mathcal{K}=\{$ &\ms{LogicalDataSet $\sqsubseteq$ dcat:DataSet},\\
 %&\ms{LogicalDataSet $\sqsubseteq \forall$ aggregation.qb:DataSet},\\
 %%&\ms{dcat:DataSet $\equiv$ $\exists$ dcat:distribution . dcat:Distribution},\\
 %&\ms{LogicalDataSet( logical-data-set )},\\
 %&\ms{aggregation( logical-data-set, aggregated-data-set )}
 %\}\\ 
%\end{DL}
%\end{center}
%
%As we know that only record-unit data sets (\emph{DDI-RDF:LogicalDataSet}) can derive (\emph{DDI-RDF:aggregation}) aggregated data sets (\emph{qb:DataSet}), 
%{\em logical-data-set} is a \emph{DDI-RDF:LogicalDataSet}, 
%and \emph{aggregated-data-set} is derived from \emph{logical-data-set},
%we conclude that \emph{aggregated-data-set} must be a \emph{qb:DataSet}.
%As \emph{aggregated-data-set} is not explicitly defined to be a \emph{qb:DataSet}, however, a constraint violation is raised.
%If we perform reasoning prior to validation, the constraint violation is resolved, as the implicit triple \ms{qb:DataSet(aggregated-data-set)} is inferred. 
%
%Reasoning may also cause constraint violations which are needed to enhance data quality.
%With \emph{subsumption} (\emph{R-100}), one can state that \emph{DDI-RDF:LogicalDataSet} is a sub-class of \emph{dcat:DataSet}, 
%i.e., each record-unit data set is also a catalog data set.
%Thus, constraints on catalog data sets are also validated for record-unit data sets;
%e.g., the \emph{existential quantification} below restricting that record-unit data sets must have a distribution:

@@

%- there should be a relationship to the underlying record-unit data.

@@

%In this paper, we showed in form of a complete real world running example how to represent metadata on record-unit data (DDI-RDF), metadata on aggregated data (QB), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
%We explained why RDF validation is important in this context and how metadata on record-unit data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}). 
%We distinguish two validation types:
%(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{SPARQL-based-constraint-types}).
%(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{vocabulary-constraint-types}).
%We determined the default \emph{severity level} for each constraint to indicate how serious the violation of the constraint is
%and propose an extensible metric to measure the continuum of severity levels.

>>>>

As we do not want to base our conclusions on the evaluation of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
For all these 115 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (DDI-RDF, QB, SKOS) obtained from 33 SPARQL endpoints.
%evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
Based on the evaluation results,
we formulate several hypotheses to direct the further development of constraint languages.
To make valid general statements for all vocabularies, however,
the hypotheses still have to be verified or falsified
by evaluating the quality of data represented by more than three vocabularies (Section \ref{evaluation}).
%The \textbf{contribution} of this paper is the development of a system 
%\begin{enumerate}
	%\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
	%\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
%\end{enumerate}
%By defining a huge amount of constraints of the majority of the constraint types,   
%we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
%A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
%We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
%how data in tabular format and metadata on unit-record data sets, aggregated data sets, and thesauri are represented in RDF, 
%how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
%and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
%We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding 
%(1) which sets of constraint types (on different levels of complexity) and 
%(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).

@@

The data most often used in research within \emph{SBE} sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records, registers of births and deaths. A \emph{study} represents the process by which a data set was generated or collected. The range of unit-record data is very broad - including census, education, health data and business, social, and labor force surveys. This type of research data is held within data archives or data libraries after it has been collected, so that it may be reused by future researchers. By its nature, unit-record data is highly confidential and access is often only permitted for qualified researchers who must apply for access. Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns: so-called \emph{variables} such as \emph{sex} or \emph{age}. Aggregated data, which answers particular research questions, is derived from unit-record data by statistics on groups or aggregates such as frequencies and arithmetic means. The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying unit-record data. For more detailed analyses, researchers refer to unit-record data including additional variables needed to answer subsequent research questions.

@@

For more detailed analyses we refer to the underlying unit-record data. The aggregated variable \emph{formal childcare} is calculated on the basis of six record-unit variables (i.a., \emph{Education at pre-school}) for which detailed metadata is given (i.a., code lists) enabling researchers to replicate the results shown in aggregated data tables.
\emph{DDI-RDF} is used to represent metadata on unit-record data in RDF.
%The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
%\emph{dcterms:spatial} points to the countries for which the data has been collected.
The study (\emph{disco:Study}) for which the unit-record data has been collected 
%\emph{EU-SILC 2011} 
contains eight data sets (\emph{disco:LogicalDataSet})
including variables (\emph{disco:Variable}) like the six ones needed to calculate the variable \emph{formal childcare}.
%Metadata on unit-record data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
%One common research question is ,e.g., the comparison of variables like 
%\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).

@@

%The data most often used in research within \emph{SBE} sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers

@@

%The range of unit-record data is very broad - 

@@

%By its nature, unit-record data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 

@@

%Aggregated data, which answers particular research questions, is derived from unit-record data by statistics on groups or aggregates such as frequencies and arithmetic means.
%The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying unit-record data.

@@

%For more detailed analyses, researchers refer to unit-record data including additional variables needed to answer subsequent research questions

@@

%For more detailed analyses we refer to the unit-record data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}. 

@@

%The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on unit-record data in RDF.

@@

%The study \emph{EU-SILC 2011} contains eight unit-record data sets (\emph{DDI-RDF:LogicalDataSet})

@@

%%Validation environments should enable users to decide if they wish to perform reasoning prior to validation.
%%Reasoning as an optional pre validation step is beneficial for RDF validation as 
%%(1) it may resolve constraint violations and  
%%(2) it may cause useful constraint violations.
%A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
%%Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
%%\begin{DL}
%%Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
%%\end{DL}
%Consider the following DL knowledge base $\mathcal{K}$\footnote{A knowledge base is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly. For simplicity reasons, we only write namespace prefixes in DL statements to avoid ambiguities.}:
%
%\begin{center}
%\begin{DL} 
%$\mathcal{K}=\{$ &\ms{LogicalDataSet $\sqsubseteq$ dcat:DataSet},\\
 %&\ms{LogicalDataSet $\sqsubseteq \forall$ aggregation.qb:DataSet},\\
 %%&\ms{dcat:DataSet $\equiv$ $\exists$ dcat:distribution . dcat:Distribution},\\
 %&\ms{LogicalDataSet( logical-data-set )},\\
 %&\ms{aggregation( logical-data-set, aggregated-data-set )}
 %\}\\ 
%\end{DL}
%\end{center}
%
%As we know that only unit-record data sets (\emph{DDI-RDF:LogicalDataSet}) can derive (\emph{DDI-RDF:aggregation}) aggregated data sets (\emph{qb:DataSet}), 
%{\em logical-data-set} is a \emph{DDI-RDF:LogicalDataSet}, 
%and \emph{aggregated-data-set} is derived from \emph{logical-data-set},
%we conclude that \emph{aggregated-data-set} must be a \emph{qb:DataSet}.
%As \emph{aggregated-data-set} is not explicitly defined to be a \emph{qb:DataSet}, however, a constraint violation is raised.
%If we perform reasoning prior to validation, the constraint violation is resolved, as the implicit triple \ms{qb:DataSet(aggregated-data-set)} is inferred. 
%
%Reasoning may also cause constraint violations which are needed to enhance data quality.
%With \emph{subsumption} (\emph{R-100}), one can state that \emph{DDI-RDF:LogicalDataSet} is a sub-class of \emph{dcat:DataSet}, 
%i.e., each unit-record data set is also a catalog data set.
%Thus, constraints on catalog data sets are also validated for unit-record data sets;
%e.g., the \emph{existential quantification} below restricting that unit-record data sets must have a distribution:

@@

%- there should be a relationship to the underlying unit-record data.

@@

%In this paper, we showed in form of a complete real world running example how to represent metadata on unit-record data (DDI-RDF), metadata on aggregated data (QB), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
%We explained why RDF validation is important in this context and how metadata on unit-record data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}). 
%We distinguish two validation types:
%(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{SPARQL-based-constraint-types}).
%(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{vocabulary-constraint-types}).
%We determined the default \emph{severity level} for each constraint to indicate how serious the violation of the constraint is
%and propose an extensible metric to measure the continuum of severity levels.

### 2015-08-12 paper/paper 2/dc-2015.tex
unit-record

It is part of future work to finalize the implementation of all 81 constraint types in our \emph{RDF Validator}, to fully map constraint languages to RDF-CV (first and foremost DSP and OWL 2) and of course keep the framework in sync with the ongoing work in the working groups.

>>>>

It is part of future work to finalize the implementation of all 81 constraint types in our \emph{RDF Validator}, to fully map constraint languages to the RDF-CV (first and foremost DSP and OWL 2), and of course to keep the framework in sync with the ongoing work in the working groups.
